---
output:
  md_document:
    variant: markdown_github
---

[![Travis-CI Build Status](https://travis-ci.org/nutterb/sillylogic.svg?branch=master)](https://travis-ci.org/nutterb/sillylogic)
[![Coverage Status](https://img.shields.io/coveralls/nutterb/sillylogic.svg)](https://coveralls.io/r/nutterb/sillylogic?branch=master)

# sillylogic

Emote via Logical Constants

Inspired by the [discussion on Twitter](https://twitter.com/michaelhoffman/status/630420081042849792), `sillylogic` provides some fun alternatives to use in place of `TRUE` and `FALSE`.  Most famously:

```{r}
devtools::install_github("nutterb/sillylogic")
library(sillylogic)
x <- data.frame(letter = letters[1:10],
                stringsAsFactors = HELLNO)
```

Which ensures that strings are not converted to factors when the data frame is assigned.

```{r}
class(x$letter)
```

## Available Logical Representations

```{r, echo=FALSE, results='asis'}
all_silly <- getNamespaceExports("sillylogic")
all_silly <- all_silly[!all_silly == "surprise_me"]
silly <- sapply(all_silly, 
                function(l) eval(parse(text = l)))

sillyTRUE <- sort(names(silly[silly]))
sillyFALSE <- sort(names(silly[!silly]))

maxlength <- max(length(sillyTRUE), length(sillyFALSE))

sillyTRUE <- c(sillyTRUE, rep("", maxlength - length(sillyTRUE)))
sillyFALSE <- c(sillyFALSE, rep("", maxlength - length(sillyFALSE)))

Silly <- cbind(sillyTRUE, sillyFALSE)
colnames(Silly) <- c("TRUE", "FALSE")

knitr::kable(Silly)
```

And for those who like to live a little dangerously, feel free to use the `surprise_me` function.

```{r}
set.seed(2)
x <- data.frame(letter = letters[1:10],
                stringsAsFactors = surprise_me())
class(x$letter)

y <- data.frame(letter = letters[1:10],
                stringsAsFactors = surprise_me())
class(y$letter)
```
